---
title: "Methods comparison Galapagos"
author: "Sara Hansen"
date: "2021-01-28"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading libraries

```{r Loading libraries, echo = FALSE}
{library(tidyverse)
library(vegan)#Question DFA - I had an error with finding function adonis, from vegan, is it because vegan was #only loaded within one of the above scripts? If this is the case, then I guess I should load tidyverse, ggplot2 #and vegan here in this markdown, instead of within one of the scripts?
library(ggsignif) #Used for level of significance in ggplots
library(pairwiseAdonis) #pairwise PERMANOVA
library(RColorBrewer) #color palette for graph
library(ggpubr)} #ggarrange, for arranging graphs
```


## Methods comparison

This markdown document is used to clean the UVC and DOVS data and compare the two methods.
Aim: Compare UVC and DOVS data in the Galapagos for predatory fish species.

### Data Cleaning
Cleaning the UVC and stereo-DOVs data.

```{r Data Cleaning}
source("1_DataCleaning.R")
```

### Unmeasured individuals in stereo-DOVs
Adding median length for a species at a site to unmeasured individuals in stereo-DOVs. 

```{r Unmeasured individuals in stereo-DOVs}
source("2_Unmeasured_DOVS.R")
```

### Calculating mean species richness, mean density and mean biomass
Calculating mean species richness, mean density and mean biomass of predatory fish species in the Galapagos per site surveyed for each of the methods UVC and stereo-DOVs.

```{r Calculating mean species richness, mean density and mean biomass}
source("3_Calculating_Richness_Density_Biomass.R")
```

### Univariate PERMANOVA for mean species richness, mean density and mean biomass
Performing univariate PERMANOVA for mean species richness, mean density and mean biomass for method (UVC and stereo-DOVs) and fishing/management status (no-take zone and fishing zone).

```{r Univariate PERMANOVA}
#UNIVARIATE PERMANOVA for species richness
perm_ric <- adonis(Site_sp_500m2 ~ Method*Fishing, data = Richness, 
                   permutations = 9999, method = "euclidean")
perm_ric

#UNIVARIATE PERMANOVA for density
perm_den <- adonis(N_site_500m2^0.5 ~ Method*Fishing, data = Density, 
                   permutations = 9999, method = "euclidean")
perm_den

#UNIVARIATE PERMANOVA for biomass
perm_bio <- adonis(Kg_500m2_site^0.25 ~ Method*Fishing, data = Biomass, 
                   permutations = 9999, method = "euclidean")
perm_bio

#Species richness univariate PERMANOVA to excel
results <- perm_ric$aov.tab
#writing excel file
write.xlsx(results, "../Tables/UNI_PERM_Richness_Boxplot.xlsx")

#Density univariate PERMANOVA to excel
results <- perm_den$aov.tab
#writing excel file
write.xlsx(results, "../Tables/UNI_PERM_Density_Boxplot.xlsx")

#Density univariate PERMANOVA to excel
results <- perm_bio$aov.tab
#writing excel file
write.xlsx(results, "../Tables/UNI_PERM_Biomass_Boxplot.xlsx")
```

### Creating boxplot for mean species richness, mean density and mean biomass
Building boxplots for mean species richness, mean density and mean biomass for UVC and stereo-DOVs. Combining boxplots into figure.

```{r Boxplot mean species richness, mean density and mean biomass}
#Boxplot of species richness with significance
Ric_boxplot <- ggplot(Richness, aes(x = Fishing, y = Site_sp_500m2, fill = Method)) +
  geom_boxplot(fatten = 3) +
  ggtitle("Mean species richness per 500"~m^2) +
  geom_signif(annotations = paste0("p = ", round(perm_ric$aov.tab$`Pr(>F)`[2], digits = 3)), 
              y_position = max(Richness$Site_sp_500m2)*1.1, 
              xmin = "Closed", xmax = "Open", textsize = 6, 
              vjust = -0.2) +
  scale_fill_manual(name = "Method", labels = c("Stereo-DOVs", "UVC"), 
                    values = grey.colors(2, start = 0.1, end = 0.5)) +
  scale_y_continuous(name = "Number of species/500"~m^2, 
                     breaks = seq(0,5,by = 1)) +
  scale_x_discrete(labels = c("No-take zone", "Fishing zone")) +
  theme_classic() +
  theme(plot.title = element_text(color="black", face="bold", hjust = 0.5),
        legend.title = element_text(color = "black", size = 17, face = "bold"), 
        legend.text = element_text(color = "black", size = 16),
        legend.key.size = unit(1.5,"cm"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(color = "black", size = 19),
        axis.text.x = element_text(color = "black", size = 18), 
        axis.text.y = element_text(color = "black", size = 18), 
        title = element_text(color = "black", size = 16),
        axis.ticks.length = unit(0.3, "cm")) +
  guides(fill = guide_legend(title.position = "top", ncol = 1)) +
  coord_cartesian(clip = "off")

Ric_boxplot

#Boxplot of density with significance
Den_boxplot <- ggplot(Density, aes(x = Fishing, y = N_site_500m2, fill = Method)) +
  geom_boxplot(fatten = 3) +
  ggtitle("Mean density per 500"~m^2) +
  geom_signif(annotations = paste0("p = ", round(perm_den$aov.tab$`Pr(>F)`[2], digits = 3)), 
              y_position = max(Density$N_site_500m2)*1.1, 
              xmin = "Closed", xmax = "Open", textsize = 6, 
              vjust = -0.2) +
  scale_fill_manual(name = "Method", labels = c("Stereo-DOVs", "UVC"), 
                    values = grey.colors(2, start = 0.1, end = 0.5)) +
  scale_y_continuous(name = "Number of individuals/500"~m^2) +
  scale_x_discrete(labels = c("No-take zone", "Fishing zone")) +
  theme_classic() +
  theme(plot.title = element_text(color="black", face="bold", hjust = 0.5),
        legend.title = element_text(color = "black"), 
        legend.text = element_text(color = "black"), 
        axis.title.x = element_blank(), 
        axis.title.y = element_text(color = "black", size = 19),
        axis.text.x = element_text(color = "black", size = 18), 
        axis.text.y = element_text(color = "black", size = 18), 
        title = element_text(color = "black", size = 16), 
        axis.ticks.length = unit(0.3, "cm")) +
  coord_cartesian(clip = "off")

Den_boxplot

#Boxplot biomass with significance
Bio_boxplot <- ggplot(Biomass, aes(x = Fishing, y = Kg_500m2_site, fill = Method)) +
  geom_boxplot(fatten = 3) + 
  ggtitle("Mean biomass per 500"~m^2) +
  geom_signif(annotations = paste0("p = ", round(perm_bio$aov.tab$`Pr(>F)`[2], digits = 3)), 
              y_position = max(Biomass$Kg_500m2_site)*1.1, 
              xmin = "Closed", xmax = "Open", textsize = 6, 
              vjust = -0.2) +
  scale_fill_manual(name = "Method", labels = c("Stereo-DOVs", "UVC"), 
                    values = grey.colors(2, start = 0.1, end = 0.5)) +
  scale_x_discrete(labels = c("No-take zone", "Fishing zone")) +
  scale_y_continuous(name = "Kg/500"~m^2) +
  theme_classic() +
  theme(plot.title = element_text(color="black", face="bold", hjust = 0.5),
        legend.title = element_text(color = "black"), 
        legend.text = element_text(color = "black"), 
        axis.title.x = element_blank(), 
        axis.title.y = element_text(color = "black", size = 19),
        axis.text.x = element_text(color = "black", size = 18), 
        axis.text.y = element_text(color = "black", size = 18), 
        title = element_text(color = "black", size = 16), 
        axis.ticks.length = unit(0.3, "cm"))+
  coord_cartesian(clip = "off")

Bio_boxplot

#Combining boxplot for richness, density and biomass
boxplot_all <- ggarrange(nrow = 1, ncol = 3, Ric_boxplot, Den_boxplot, Bio_boxplot,
                         align = "v", common.legend = TRUE, legend = "right")
boxplot_all

#Saving composite image with different ratios
ggsave("../Figures/CompBoxplot.tiff", boxplot_all, device = "tiff", dpi = 300, width = 18, height = 6.5)


#Delete variables used for boxplots
rm(boxplot_all, Ric_boxplot, Den_boxplot, Bio_boxplot)
#Remove Univariate PERMANOVA variables
rm(perm_ric, perm_den, perm_bio, results)
```


### Creating boxplot for bioregions and mean species richness, mean density and mean biomass
Building boxplots for bioregions for mean species richness, mean density and mean biomass for UVC and stereo-DOVs. Combining boxplots into figure.

```{r Boxplot for bioregions}
#Making a dataframe for the boxplot
Bioreg <- Richness %>% 
  #Adding density column
  left_join(Density %>% select(Site, Method, N_site_500m2), by = c("Site", "Method")) %>% 
  #Adding biomass column
  left_join(Biomass %>% select(Site, Method, Kg_500m2_site), by = c("Site", "Method")) %>% 
  #Adding bioregion data from SiteInfo
  #left_join(SiteInfo %>% select(Site, Bioregion) %>% unique(), by = "Site") %>% 
  #reordering columns
  select(Site, Site_sp_500m2, N_site_500m2, Kg_500m2_site, Bioregion, everything()) %>% 
  rename(Zone = Fishing) %>% 
  #renaming bioregions
  mutate(Bioregion = recode(Bioregion, 
                            "Lejano Norte" = "Far Northern", 
                            "Norte" = "Northern", 
                            "Centro Sur" = "Central South-eastern", 
                            "Oeste Fria" = "Western")) %>% 
  #column with combined bioregion and zone
  mutate(Bioreg_zone = paste(Bioregion, Zone))

#Boxplot bioregion and species richness with significance
Bioreg_ric <- ggplot(Bioreg, aes(x = Zone, y = Site_sp_500m2, fill = Bioregion)) +
  geom_boxplot(fatten = 3) +
  ggtitle("Mean species richness per 500"~m^2) +
  scale_y_continuous(name = "Number of species/500"~m^2) +
  scale_x_discrete(labels = c("No-take zone", "Fishing zone")) +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  theme(plot.title = element_text(color="black", face="bold", hjust = 0.5),
        legend.title = element_text(color = "black", size = 17, face = "bold"), 
        legend.text = element_text(color = "black", size = 16),
        legend.key.size = unit(1.5,"cm"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(color = "black", size = 19),
        axis.text.x = element_text(color = "black", size = 18), 
        axis.text.y = element_text(color = "black", size = 18), 
        title = element_text(color = "black", size = 15), 
        axis.ticks.length = unit(0.3, "cm")) +
  guides(fill = guide_legend(title.position = "top", ncol = 1)) +
  coord_cartesian(clip = "off")

Bioreg_ric

#Boxplot bioregion and density with significance
Bioreg_den <- ggplot(Bioreg, aes(x = Zone, y = N_site_500m2, fill = Bioregion)) +
  geom_boxplot(fatten = 3) +
  ggtitle("Mean density per 500"~m^2) +
  scale_y_continuous(name = "Number of individuals/500"~m^2) +
  scale_x_discrete(labels = c("No-take zone", "Fishing zone")) +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  theme(plot.title = element_text(color="black", face="bold", hjust = 0.5),
        legend.title = element_text(color = "black"), 
        legend.text = element_text(color = "black"), 
        axis.title.x = element_blank(), 
        axis.title.y = element_text(color = "black", size = 19),
        axis.text.x = element_text(color = "black", size = 18), 
        axis.text.y = element_text(color = "black", size = 18), 
        title = element_text(color = "black", size = 15), 
        axis.ticks.length = unit(0.3, "cm")) +
  coord_cartesian(clip = "off")

Bioreg_den

#Boxplot bioregion and biomass
Bioreg_bio <- ggplot(Bioreg, aes(x = Zone, y = Kg_500m2_site, fill = Bioregion)) +
  geom_boxplot(fatten = 3) + 
  ggtitle("Mean biomass per 500"~m^2) +
  scale_x_discrete(labels = c("No-take zone", "Fishing zone")) +
  scale_y_continuous(name = "Kg/500"~m^2) +
  scale_fill_brewer(palette = "Dark2") +
  theme_classic() +
  theme(plot.title = element_text(color="black", face="bold", hjust = 0.5),
        legend.title = element_text(color = "black"), 
        legend.text = element_text(color = "black"), 
        axis.title.x = element_blank(), 
        axis.title.y = element_text(color = "black", size = 19),
        axis.text.x = element_text(color = "black", size = 18), 
        axis.text.y = element_text(color = "black", size = 18), 
        title = element_text(color = "black", size = 15), 
        axis.ticks.length = unit(0.3, "cm"))+
  coord_cartesian(clip = "off")

Bioreg_bio

#Combining boxplot for richness, density and biomass
boxplot_bioreg <- ggarrange(nrow = 1, ncol = 3, Bioreg_ric, Bioreg_den, Bioreg_bio,
                         align = "v", common.legend = TRUE, legend = "right")
boxplot_bioreg

#Saving composite image with different ratios - DFA
ggsave("../Figures/boxplot_bioreg.tiff", boxplot_bioreg, device = "tiff", dpi = 300, width = 18, height = 6.5)
```

### Univariate PERMANOVA for bioregions
Performing univariate PERMANOVA for bioregions and mean species richness, mean density and mean biomass for methods (UVC and stereo-DOVs) and fishing/management status (no-take zone and fishing zone).

Question DFA - should I instead do a pairwise adonis for all combinations? 
Then I would get each of the sites compared for no-take and fishing zones (which I do not currently have)

```{r Univariate PERMANOVA for bioregions}
### Richness ###

#UNIVARIATE PERMANOVA for species richness
perm_ric <- adonis(Site_sp_500m2 ~ Zone*Bioregion, data = Bioreg, 
                   permutations = 9999, method = "euclidean")
perm_ric
perm_ric2 <- as.data.frame(perm_ric$aov.tab)

#No take pairwise adonis
No_take_bioreg <- Bioreg %>% filter(Zone == "Closed")
pair_adonis1 <- pairwise.adonis(No_take_bioreg[,"Site_sp_500m2"], No_take_bioreg$Bioreg_zone, 
                                sim.method = "euclidean", perm = 9999)
pair_adonis1 <- as.data.frame(pair_adonis1)
#Question - write code to save to excel - depending on what pairwise adonis should be done

#No take pairwise adonis
Fishing_bioreg <- Bioreg %>% filter(Zone == "Open")
pair_adonis2 <- pairwise.adonis(Fishing_bioreg[,"Site_sp_500m2"], Fishing_bioreg$Bioreg_zone, 
                                sim.method = "euclidean", perm = 9999)
pair_adonis2 <- as.data.frame(pair_adonis2)

#Question DFA - is it correct that I cannot do betadispersion on a univariate PERMANOVA?

### Density ###

#UNIVARIATE PERMANOVA for density 
perm_den <- adonis(N_site_500m2^0.5 ~ Zone*Bioregion, data = Bioreg, 
                   permutations = 9999, method = "euclidean")
perm_den
perm_den2 <- as.data.frame(perm_den$aov.tab)

#No take pairwise adonis
#Question DFA - should I also do the transformation in the pairwise adonis?
pair_adonis3 <- pairwise.adonis(No_take_bioreg[,"N_site_500m2"]^0.5, No_take_bioreg$Bioreg_zone, 
                                sim.method = "euclidean", perm = 9999)
pair_adonis3 <- as.data.frame(pair_adonis3)

#Fishing pairwise adonis
pair_adonis4 <- pairwise.adonis(Fishing_bioreg[,"N_site_500m2"]^0.5, Fishing_bioreg$Bioreg_zone, 
                                sim.method = "euclidean", perm = 9999)
pair_adonis4 <- as.data.frame(pair_adonis4)


### Biomass ###

#UNIVARIATE PERMANOVA for biomass
perm_bio <- adonis(Kg_500m2_site^0.25 ~ Zone*Bioregion, data = Bioreg, 
                   permutations = 9999, method = "euclidean")
perm_bio
perm_bio2 <- as.data.frame(perm_bio$aov.tab)

#No take pairwise adonis
pair_adonis5 <- pairwise.adonis(No_take_bioreg[,"Kg_500m2_site"], No_take_bioreg$Bioreg_zone, 
                                sim.method = "euclidean", perm = 9999)
pair_adonis5 <- as.data.frame(pair_adonis5)

#Fishing pairwise adonis
pair_adonis6 <- pairwise.adonis(Fishing_bioreg[,"Kg_500m2_site"], Fishing_bioreg$Bioreg_zone, 
                                sim.method = "euclidean", perm = 9999)
pair_adonis6 <- as.data.frame(pair_adonis6)

#Write to excel before deleting
#Delete variables used for boxplots
rm(Bioreg, boxplot_bioreg, Bioreg_ric, Bioreg_den, Bioreg_bio)

#Deleting permanova and pairwise.adonis variables
rm(perm_ric, perm_den, perm_bio, pair_adonis1, pair_adonis2, pair_adonis3, 
   pair_adonis4, pair_adonis5, pair_adonis6, No_take_bioreg, Fishing_bioreg)
```

### Calculations for PCO on biomass data
Preparing biomass data for PCO and performing PCO calculations. 
A function is used to compute arrows for to enable them to be added on the final ggplot of PCO biomass data.

```{r Calculations PCO biomass}
source("4_Calculations_PCO_biomass.R")
```

### PCO plot for biomass data, method and management zonation
Plotting Principal Coordinates analysis (PCO) for biomass of predatory fish species with indicated method (UVC and stereo-DOVs) and management zonation (Fishing zone or No-take zone).

```{r PCO biomass, method and management zonation, echo=FALSE}
# PCO Figure for biomass Method and Bioregion -----------------------------

#Question - change depending on the species we keep after pearson correlation corrections.
#Plotting biomass, method, fishing and arrows for species with largest biomass
PCO_bio_1 <- ggplot(PCO_biomass) + 
  #Adding color for fishing and shapes for method
  geom_point(aes(PC1, PC2, color = Method, shape = Zone), stroke = 2, size = 4.5) + 
  scale_color_manual(values = brewer.pal(8, "Dark2")[c(5,8)]) +
  scale_shape_manual(values = c(21,24)) +
  guides(color = guide_legend(order = 1), 
         shape = guide_legend(order = 2)) +
  geom_segment(data = arrows_df, #Adding arrows
               x = Anchor[1], y = Anchor[2],
               mapping = aes(xend = X2, yend = Y2),
               arrow = arrow(length = unit(2, "mm")), #Adding arrow head
               size = 0.8) +
  #Adding arrow labels for C. galapagensis
  geom_text(data = arrows_df[6,], aes(label = arrows_df$variable[6]),
            size = 7, fontface = "italic",
            lineheight = 0.6, 
            x = X2[6], y = Y2[6], 
            hjust = 0.1, vjust = -0.4) +
  #Adding arrow labels for S. lewini
  geom_text(data = arrows_df[7,], aes(label = arrows_df$variable[7]),
            size = 7, fontface = "italic",
            lineheight = 0.6, 
            x = X2[7], y = Y2[7], 
            hjust = 0.5, vjust = -0.5) +
  #Adding arrow labels for L. argentiventris
  geom_text(data = arrows_df[1,], aes(label = arrows_df$variable[1]),
            size = 7, fontface = "italic",
            lineheight = 0.6, 
            x = X2[1], y = Y2[1], 
            hjust = 0.5, vjust = 1.2) +
  #Changing axes and color
  scale_x_continuous(breaks = seq(-0.6, 0.6, by = 0.3), limits = c(-0.6, 0.6)) +
  scale_y_continuous(breaks = seq(-0.3, 0.6, by = 0.3), limits = c(-0.35, 0.6)) +
  theme_classic() +
  #Adding percentages for the PCO axes
  xlab(paste0("PCO1 (", 
              as.character(as.numeric(format(round(Bio_mat_pcoa$values$Relative_eig[1], 3)))*100), 
              "% of total variation)")) +
  ylab(paste0("PCO2 (", 
              as.character(as.numeric(format(round(Bio_mat_pcoa$values$Relative_eig[2], 3)))*100), 
              "% of total variation)")) +
  #moving legend in plot and making box around it
  theme(legend.position = c(0.85, 0.85), 
        legend.box.background = element_rect(size = 0.7, linetype = "solid", colour ="black"), 
        legend.box.margin = margin(0.1, 0.1, 0.1, 0.1, "cm"),
        legend.title = element_text(color = "black", size = 23),
        legend.text = element_text(color = "black", size = 21),
        axis.text.x = element_text(color = "black", size = 23), 
        axis.text.y = element_text(color = "black", size = 23), 
        axis.title.x = element_text(color = "black", size = 25),
        axis.title.y = element_text(color = "black", size = 25), 
        axis.line.x = element_line(color = "black", size = 1), 
        axis.line.y = element_line(color = "black", size = 1), 
        axis.ticks = element_line(color = "black", size = 1.2), 
        axis.ticks.length = unit(0.2, "cm"))

PCO_bio_1

#Saving PCO for biomass - method and management status
ggsave("../Figures/PCO_bio_method_fishing.tiff", 
       PCO_bio_1, device = "tiff", dpi = 300, width = 11, height = 10)
```

### PCO plot for biomass data, bioregion and management zonation
Plotting Principal Coordinates analysis (PCO) for biomass of predatory fish species with indicated Bioregion (Central South-eastern, Far Northern, Northern and Western) and management zonation (Fishing zone or No-take zone).

```{r PCO biomass, bioregion and management zonation, echo=FALSE}
#plotting biomass, Bioregion and fishing, along with arrows for species with largest biomasses
PCO_bio_2 <- ggplot(PCO_biomass) + 
  geom_point(aes(PC1, PC2, color = Bioregion, shape = Zone), stroke = 2, size = 4.5) + 
  scale_color_brewer(palette = "Dark2") +
  scale_shape_manual(values = c(21,24)) +
  guides(color = guide_legend(order = 1), 
         shape = guide_legend(order = 2)) +
  geom_segment(data = arrows_df, #Adding arrows
               x = Anchor[1], y = Anchor[2],
               mapping = aes(xend = X2, yend = Y2),
               arrow = arrow(length = unit(2, "mm")), #Adding arrow head
               size = 0.8) +
  #Adding arrow labels for C. galapagensis
  geom_text(data = arrows_df[6,], aes(label = arrows_df$variable[6]),
            size = 7, fontface = "italic",
            lineheight = 0.6, 
            x = X2[6], y = Y2[6], 
            hjust = 0.1, vjust = -0.4) +
  #Adding arrow labels for S. lewini
  geom_text(data = arrows_df[7,], aes(label = arrows_df$variable[7]),
            size = 7, fontface = "italic",
            lineheight = 0.6, 
            x = X2[7], y = Y2[7], 
            hjust = 0.5, vjust = -0.5) +
  #Adding arrow labels for L. argentiventris
  geom_text(data = arrows_df[1,], aes(label = arrows_df$variable[1]),
            size = 7, fontface = "italic",
            lineheight = 0.6, 
            x = X2[1], y = Y2[1], 
            hjust = 0.5, vjust = 1.2) +
  #Changing axes and color
  scale_x_continuous(breaks = seq(-0.6, 0.6, by = 0.3), limits = c(-0.6, 0.6)) +
  scale_y_continuous(breaks = seq(-0.3, 0.6, by = 0.3), limits = c(-0.35, 0.6)) +
  theme_classic() +
  #Adding percentages for the PCO axes
  xlab(paste0("PCO1 (", 
              as.character(as.numeric(format(round(Bio_mat_pcoa$values$Relative_eig[1], 3)))*100), 
              "% of total variation)")) +
  ylab(paste0("PCO2 (", 
              as.character(as.numeric(format(round(Bio_mat_pcoa$values$Relative_eig[2], 3)))*100), 
              "% of total variation)")) +
  #moving legend in plot and making box around it
  theme(legend.position = c(0.82, 0.82), 
        legend.box.background = element_rect(size = 0.7, linetype = "solid", colour ="black"), 
        legend.box.margin = margin(0.1, 0.1, 0.1, 0.1, "cm"),
        legend.title = element_text(color = "black", size = 23),
        legend.text = element_text(color = "black", size = 21),
        axis.text.x = element_text(color = "black", size = 23), 
        axis.text.y = element_text(color = "black", size = 23), 
        axis.title.x = element_text(color = "black", size = 25),
        axis.title.y = element_text(color = "black", size = 25), 
        axis.line.x = element_line(color = "black", size = 1), 
        axis.line.y = element_line(color = "black", size = 1), 
        axis.ticks = element_line(color = "black", size = 1.2), 
        axis.ticks.length = unit(0.2, "cm"))

PCO_bio_2


#Saving PCO for biomass - method and fishing status
ggsave("Figures/PCO_bio_bioregion_fishing.tiff", 
       PCO_bio_2, device = "tiff", dpi = 300, width = 11, height = 10)


#remove unnecessary variables
rm(compute_arrows, species_pcoa_arrows, arrows_df, Anchor, K, X2, Y2)
rm(Bio_mat_pco, Bio_mat_pcoa, PCO_bio_1, PCO_bio_2)
```

### Multivariate PERMANOVA for biomass data
Performing multivariate PERMANOVA for fourth root transformed biomass data and method (UVC and stereo-DOVs), bioregion (Central South-eastern, Far Northern, Northern and Western) and management zone (no-take and fishing).

```{r PERMANOVA biomass}
#Data frame for PERMANOVA Factors to be tested
Factors <- Biomass %>% 
  left_join(Richness %>% select(Site, Method, Site_sp_500m2), #joining richness data
            by = c("Site", "Method")) %>% 
  left_join(Density %>% select(Site, Method, N_site_500m2), #joining density data
            by = c("Site", "Method")) %>% 
  left_join(SiteInfo %>% select(Site, Bioregion, Island) %>% unique(), by = "Site") %>% 
  ungroup() %>% #Ungrouping, as site is grouped to something.
  mutate_if(is.character, as.factor) %>% 
  arrange(Site)
#Checking type of data for all columns in Factors
str(Factors)

#PERMANOVA Main effects and interactions
perm1 <- adonis(Bio_mat ~ Method*Fishing*Bioregion,
                data = Factors, method = "bray", permutations = 9999)
perm1

#Betadispersion Fishing status
dispersion <- betadisper(Bio_mat_dist, group = Factors$Fishing)
beta_perm1 <- permutest(dispersion, permutations = 9999)
beta_perm1
#Non-significant

#Betadispersion Bioregion
dispersion <- betadisper(Bio_mat_dist, group = Factors$Bioregion)
beta_perm2 <- permutest(dispersion, permutations = 9999)
beta_perm2
#Significant

#Pairwise PERMANOVA to test which of the bioregions differ significantly from each other
pair_adonis <- pairwise.adonis(Bio_mat_dist, Factors$Bioregion, perm = 9999)
pair_adonis

#Question - write to excel in script?

#Excel sheet with PERMANOVA results for method, fishing, bioregion
results <- list(perm1$aov.tab)
#writing excel sheet
write.xlsx(results, "../Tables/PERMANOVA_PCO_bio_met_fish_bioreg.xlsx")

#Excel sheet with BETADISPERSION results for fishing
results <- list(beta_perm1$tab)
#writing excel sheet
write.xlsx(results, "../Tables/BETADISPERSION_PCO_biomass_fish.xlsx")

#Excel sheet with BETADISPERSION results for bioregion
results <- list(beta_perm2$tab)
#writing excel sheet
write.xlsx(results, "../Tables/BETADISPERSION_PCO_biomass_bioreg.xlsx")


#Excel sheet with PAIRWISE PERMANOVA results for bioregion
results <- list(pair_adonis)
#writing excel sheet
write.xlsx(results, "../Tables/PAIR_ADONIS_PCO_biomass_bioreg.xlsx")


#Removing unnecessary variables
rm(dispersion, Bio_mat_dist, perm1, beta_perm1, beta_perm2, pair_adonis)
```

### Calculations for PCO on density data
Preparing density data for PCO and performing PCO calculations. 
A function is used to compute arrows for to enable them to be added on the final ggplot of PCO density data.

```{r Calculations PCO biomass}
source("5_Calculations_PCO_density.R")
```

### PCO plot for density data, method and management zonation
Plotting Principal Coordinates analysis (PCO) for density of predatory fish species with indicated method (UVC and stereo-DOVs) and management zonation (Fishing zone or No-take zone).

```{r PCO density, method and management zonation, echo=FALSE}
#plotting density, method, fishing and arrows for species with largest densities
PCO_den_1 <- ggplot(PCO_density) + 
  #Adding color for fishing and shapes for method
  geom_point(aes(PC1, PC2, fill = Zone, shape = Method, stroke = 1.5), size = 4.5) + 
  scale_fill_manual(values = c(NA, "black")) +
  scale_shape_manual(values = c(21,24)) +
  guides(fill = guide_legend(override.aes = list(shape = 21)), 
         shape = guide_legend(override.aes = list(fill = "black"))) +
  geom_segment(data = arrows_df, #Adding arrows
               x = Anchor[1], y = Anchor[2],
               mapping = aes(xend = X2, yend = Y2),
               arrow = arrow(length = unit(2, "mm")), #Adding arrow head
               size = 0.8) +
  #Adding arrow labels for L. argentiventris
  geom_text(data = arrows_df[1,], aes(label = arrows_df$variable[1]),
            size = 7, fontface = "italic",
            lineheight = 0.6, 
            x = X2[1], y = Y2[1], 
            hjust = 0.9, vjust = -0.5) +
  #Adding arrow labels for M. olfax
  geom_text(data = arrows_df[3,], aes(label = arrows_df$variable[3]),
            size = 7, fontface = "italic",
            lineheight = 0.6, 
            x = X2[3], y = Y2[3], 
            hjust = 0.5, vjust = -0.5) +
  #Adding arrow labels for S. lewini
  geom_text(data = arrows_df[6,], aes(label = arrows_df$variable[6]),
            size = 7, fontface = "italic",
            lineheight = 0.6, 
            x = X2[6], y = Y2[6], 
            hjust = 0.4, vjust = 1.5) +
  #Changing scales and color of plot
  scale_color_grey(start = 0.1, end = 0.5) +
  theme_classic() +
  #Adding percentages for the PCO axes
  xlab(paste0("PCO1 (", 
              as.character(as.numeric(format(round(Den_mat_pcoa$values$Relative_eig[1], 3)))*100), 
              "% of total variation)")) +
  ylab(paste0("PCO2 (", 
              as.character(as.numeric(format(round(Den_mat_pcoa$values$Relative_eig[2], 3)))*100), 
              "% of total variation)")) +
  #moving legend in plot and making box around it
  theme(legend.position = c(0.85, 0.85), 
      legend.box.background = element_rect(size = 0.7, linetype = "solid", colour ="black"), 
      legend.box.margin = margin(0.1, 0.1, 0.1, 0.1, "cm"),
      legend.title = element_text(color = "black", size = 23),
      legend.text = element_text(color = "black", size = 21),
      axis.text.x = element_text(color = "black", size = 23), 
      axis.text.y = element_text(color = "black", size = 23), 
      axis.title.x = element_text(color = "black", size = 25),
      axis.title.y = element_text(color = "black", size = 25), 
      axis.line.x = element_line(color = "black", size = 1), 
      axis.line.y = element_line(color = "black", size = 1), 
      axis.ticks = element_line(color = "black", size = 1.2), 
      axis.ticks.length = unit(0.2, "cm"))

PCO_den_1

#Saving PCO for biomass - method and fishing status
ggsave("Figures/PCO_den_method_fishing.tiff", 
       PCO_den_1, device = "tiff", dpi = 300, width = 11, height = 10)
```

### PCO plot for density data, bioregion and management zonation
Plotting Principal Coordinates analysis (PCO) for density of predatory fish species with indicated Bioregion (Central South-eastern, Far Northern, Northern and Western) and management zonation (Fishing zone or No-take zone).

```{r PCO density, bioregion and management zonation, echo=FALSE}
#plotting biomass, method, fishing and arrows for species with largest biomasses
PCO_den_2 <- ggplot(PCO_density) +
  #Adding color for fishing and shapes for method
  geom_point(aes(PC1, PC2, fill = Zone, shape = Bioregion), stroke = 1.5, size = 4.5) + 
  scale_fill_manual(values = c(NA, "black")) +
  scale_shape_manual(values = c(21,24, 22, 23)) +
  guides(fill = guide_legend(override.aes = list(shape = 21)), 
         shape = guide_legend(override.aes = list(fill = "black"))) +
  geom_segment(data = arrows_df, #Adding arrows
               x = Anchor[1], y = Anchor[2],
               mapping = aes(xend = X2, yend = Y2),
               arrow = arrow(length = unit(2, "mm")), #Adding arrow head
               size = 0.8) +
  #Adding arrow labels for L. argentiventris
  geom_text(data = arrows_df[1,], aes(label = arrows_df$variable[1]),
            size = 7, fontface = "italic",
            lineheight = 0.6, 
            x = X2[1], y = Y2[1], 
            hjust = 0.9, vjust = -0.5) +
  #Adding arrow labels for M. olfax
  geom_text(data = arrows_df[3,], aes(label = arrows_df$variable[3]),
            size = 7, fontface = "italic",
            lineheight = 0.6, 
            x = X2[3], y = Y2[3], 
            hjust = 0.5, vjust = -0.5) +
  #Adding arrow labels for S. lewini
  geom_text(data = arrows_df[6,], aes(label = arrows_df$variable[6]),
            size = 7, fontface = "italic",
            lineheight = 0.6, 
            x = X2[6], y = Y2[6], 
            hjust = 0.4, vjust = 1.5) +
  #Changing scales and color of plot
  #scale_x_continuous(breaks = seq(-0.6, 0.6, by = 0.3), limits = c(-0.6, 0.65)) +
  scale_color_grey(start = 0.1, end = 0.5) +
  theme_classic() +
  #Adding percentages for the PCO axes
  xlab(paste0("PCO1 (", 
              as.character(as.numeric(format(round(Den_mat_pcoa$values$Relative_eig[1], 3)))*100), 
              "% of total variation)")) +
  ylab(paste0("PCO2 (", 
              as.character(as.numeric(format(round(Den_mat_pcoa$values$Relative_eig[2], 3)))*100), 
              "% of total variation)")) +
  #moving legend in plot and making box around it
  #moving legend in plot and making box around it
  theme(legend.position = c(0.82, 0.82), 
        legend.box.background = element_rect(size = 0.7, linetype = "solid", colour ="black"), 
        legend.box.margin = margin(0.1, 0.1, 0.1, 0.1, "cm"),
        legend.title = element_text(color = "black", size = 23),
        legend.text = element_text(color = "black", size = 21),
        axis.text.x = element_text(color = "black", size = 23), 
        axis.text.y = element_text(color = "black", size = 23), 
        axis.title.x = element_text(color = "black", size = 25),
        axis.title.y = element_text(color = "black", size = 25), 
        axis.line.x = element_line(color = "black", size = 1), 
        axis.line.y = element_line(color = "black", size = 1), 
        axis.ticks = element_line(color = "black", size = 1.2), 
        axis.ticks.length = unit(0.2, "cm"))

PCO_den_2

#Saving PCO for biomass - method and fishing status
ggsave("Figures/PCO_den_fishing_bioregion.tiff", 
       PCO_den_2, device = "tiff", dpi = 300, width = 11, height = 10)


#remove unnecessary variables
rm(compute_arrows, species_pcoa_arrows, arrows_df, Anchor, K, X2, Y2)
rm(Den_mat_pco, Den_mat_pcoa, PCO_den_1, PCO_den_2)
```


### Multivariate PERMANOVA for density data
Performing multivariate PERMANOVA for square root transformed density data and method (UVC and stereo-DOVs), bioregion (Central South-eastern, Far Northern, Northern and Western) and management zone (no-take and fishing).

```{r PERMANOVA density}
#PERMANOVA Main effects and interactions
perm1 <- adonis(Den_mat ~ Method*Fishing*Bioregion,
                data = Factors, method = "bray", permutations = 9999)
perm1

#Betadispersion Bioregion
dispersion <- betadisper(Den_mat_dist, group = Factors$Bioregion)
beta_perm1 <- permutest(dispersion, permutations = 9999)
beta_perm1
#Non-significant

#Betadispersion fishing
dispersion <- betadisper(Den_mat_dist, group = Factors$Fishing)
beta_perm2 <- permutest(dispersion, permutations = 9999)
beta_perm2
#Non-significant

#Pairwise PERMANOVA to test which of the bioregions differ significantly from each other
pair_adonis <- pairwise.adonis(Den_mat_dist, Factors$Bioregion, perm = 9999)
pair_adonis

#Removing unnecessary variables
rm(dispersion, Den_mat, Den_mat_dist)


#Excel sheet with PERMANOVA results for method, fishing, bioregion
results <- perm1$aov.tab
#writing excel sheet
write.xlsx(results, "../Tables/PERMANOVA_PCO_den_met_fish_bioreg.xlsx")

#Excel sheet with BETADISPERSION results for bioregion
results <- list(beta_perm1$tab)
#writing excel sheet
write.xlsx(results, "../Tables/BETADISPERSION_PCO_den_bioreg.xlsx")

#Excel sheet with BETADISPERSION results for fishing
results <- list(beta_perm2$tab)
#writing excel sheet
write.xlsx(results, "../Tables/BETADISPERSION_PCO_den_fishing.xlsx")

#Excel sheet with PAIRWISE PERMANOVA results for bioregion
results <- list(pair_adonis)
#writing excel sheet
write.xlsx(results, "../Tables/PAIR_ADONIS_PCO_den_bioreg.xlsx")


#Removing unnecessary variables
rm(perm1, beta_perm1, beta_perm2, pair_adonis)
```

### Species list and study site descriptors
Creating species list and study site descriptors data frames and writing them to excel.

```{r Species list and study site descriptors}
source("6_SpeciesList_SiteDescriptors.R")
```

